Global optimization method with dual Lipschitz constant estimates for problems with non-convex constraints\thanks{This research was supported by the Russian Science Foundation, project No. 16-11-10150.}

### 2020-05-27 2019/NUMTA_Barkalov/SoftComputing/article.tex

\smartqed  % flush right qed marks, e.g. at end of proof
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{hyperref,amsmath}
\usepackage[pagewise]{lineno}
\usepackage{multirow}
\usepackage[round]{natbib} 
\usepackage[misc]{ifsym}
\usepackage{xcolor}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

@@

		Several typical methods for adaptive estimation of the Lipschitz constant according to the results of the performed search trials are known:
\begin{itemize}
\item global estimate of the constant $L$ in the whole search domain $D$ (\cite{Strongin2000,Pinter1996,Horst1996}).
\item local estimates of the constants $L_i$ in different subdomains $D_i$ of the search domain $D$ (\cite{Sergeyev1998,Kvasov2003,Sergeyev2010,Sergeyev2016}).
\item choice of the estimates of the constant $L$ from some set of possible values (\cite{Jones2009,Jones1993,Gablonsky2001,Sergeyev2006}).
\end{itemize}

@@

	Along with the exact solution $y^\ast$ of the problem (\ref{problem}), we will consider also the $\varepsilon$-reserved solution $y_{\epsilon}$, for which 
\small
\begin{align}\label{epsilon_reserved_solution}
	\varphi(y_{\epsilon}) = \min{\left\{\varphi(y):y \in D, g_j(y)\leq -{\epsilon}_j, 1 \leq j \leq m\right\}},
\end{align}
\normalsize
where the algorithm parameters $\epsilon_j, \; 1\leq j \leq m,$ are non negative numbers, and the set of solutions $Y_{\epsilon}$, which are not worse than the $\varepsilon$-reserved solution in the objective function value, i.e.
\small
\begin{align}\label{Y_epsilon}
	Y_{\epsilon} = \left\{ y \in D, \; g_j(y) \leq 0, \; 1 \leq j \leq m, \; \varphi(y) \leq \varphi(y_{\epsilon}) \right\}.
\end{align}
\normalsize
Fig. \ref{fig:eps_reserved_solution} illustrates the concepts introduced.
{\color{red} The figure shows global minimizer $y^*$, $\epsilon$-reserved solution $y_\epsilon$ and the set $Y_\epsilon$ of all admissible points which are not worse than the $\epsilon$-reserved solution. }

\begin{figure}
	\center{\includegraphics[width=0.6\linewidth]{Fig1.pdf}}
	\caption{ {\color{red} An $\varepsilon$-reserved solution to a two-dimensional problem. } }
	\label{fig:eps_reserved_solution}
\end{figure}

@@

	We will consider the initial problem (\ref{problem}) assuming that the problem functions $g_{j}(y)$, $1 \leq j \leq m+1$, may be defined only partly. It means that they are defined and computable only in the sets
\small
\begin{align}\label{D_sets}
	D_1 = D, \; D_{j+1} = \left\{ y \in D_j: \; g_j(y) \leq 0 \right\}, \; 1 \leq j \leq m.
\end{align}
\normalsize
This situation is typical for the optimal design problems when some conditions for the functioning of the modeled object are not met and its other characteristics appear to be undefined. 
{\color{red} In this approach, the violation of any constraint at the point $y$ terminates the computation of the values of other functions at this point. }

@@

	In \cite{Gergel2017_2,Gergel2019}, an approach was proposed that allows constructing the constrained global optimization problems using certain classes of multiextremal functions (in particular, the GKLS functions), in which:
\begin{itemize}
  \item the number of constraints can be varied;
  \item the volume of the feasible subdomain $Q_{m+1}$ relative to the whole search domain $D$ is defined;
	\item the global minimizer is known in advance and can be located at the boundary of the feasible domain;
	\item {\color{red} the number of constraints active at the global minimizer can be predefined (an inequality constraint is called active at some point if at this point the inequality turns into equality)}.
\end{itemize}

>>>>

\smartqed  % flush right qed marks, e.g. at end of proof
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{hyperref,amsmath}
%\usepackage[pagewise]{lineno}
\usepackage{multirow}
\usepackage[round]{natbib} 
\usepackage[misc]{ifsym}
%\usepackage{xcolor}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

@@

		Several typical methods for adaptive estimation of the Lipschitz constant according to the results of the performed search trials are known:
\begin{itemize}
\item global estimate of the constant $L$ in the whole search domain $D$ (\cite{Strongin2000,Pinter1996,Horst1996}).
\item local estimates of the constants $L_i$ in different subdomains $D_i$ of the search domain $D$ (\cite{Sergeyev1998,Kvasov2003,Sergeyev2010}, \cite{Sergeyev2016}).
\item choice of the estimates of the constant $L$ from some set of possible values (\cite{Jones2009,Jones1993,Gablonsky2001,Sergeyev2006}).
\end{itemize}

@@

	Along with the exact solution $y^\ast$ of the problem (\ref{problem}), we will consider also the $\varepsilon$-reserved solution $y_{\epsilon}$, for which 
\small
\begin{align}\label{epsilon_reserved_solution}
	\varphi(y_{\epsilon}) = \min{\left\{\varphi(y):y \in D, g_j(y)\leq -{\epsilon}_j, 1 \leq j \leq m\right\}},
\end{align}
\normalsize
where the algorithm parameters $\epsilon_j, \; 1\leq j \leq m,$ are non negative numbers, and the set of solutions $Y_{\epsilon}$, which are not worse than the $\varepsilon$-reserved solution in the objective function value, i.e.
\small
\begin{align}\label{Y_epsilon}
	Y_{\epsilon} = \left\{ y \in D, \; g_j(y) \leq 0, \; 1 \leq j \leq m, \; \varphi(y) \leq \varphi(y_{\epsilon}) \right\}.
\end{align}
\normalsize
Fig. \ref{fig:eps_reserved_solution} illustrates the concepts introduced above.
The figure shows the global minimizer $y^*$, the $\epsilon$-reserved solution $y_\epsilon$ and the set $Y_\epsilon$ of all admissible points which are not worse than the $\epsilon$-reserved solution.

\begin{figure}
	\center{\includegraphics[width=0.6\linewidth]{Fig1.pdf}}
	\caption{ An $\varepsilon$-reserved solution to a two-dimensional problem }
	\label{fig:eps_reserved_solution}
\end{figure}

@@

	We will consider the initial problem (\ref{problem}) assuming that the problem functions $g_{j}(y)$, $1 \leq j \leq m+1$, may be defined only partly. It means that they are defined and computable only in the sets
\small
\begin{align}\label{D_sets}
	D_1 = D, \; D_{j+1} = \left\{ y \in D_j: \; g_j(y) \leq 0 \right\}, \; 1 \leq j \leq m.
\end{align}
\normalsize
This situation is typical for the optimal design problems when some conditions for the functioning of the modeled object are not met and its other characteristics appear to be undefined. 
In this approach, the violation of any constraint at the point $y$ terminates the computation of the values of other functions at this point.

@@

	In \cite{Gergel2017_2,Gergel2019}, an approach was proposed that allows constructing the constrained global optimization problems using certain classes of multiextremal functions (in particular, the GKLS functions), in which:
\begin{itemize}
  \item the number of constraints can be varied;
  \item the volume of the feasible subdomain $Q_{m+1}$ relative to the whole search domain $D$ is defined;
	\item the global minimizer is known in advance and can be located at the boundary of the feasible domain;
	\item the number of constraints active at the global minimizer can be predefined (an inequality constraint is called active at some point if at this point the inequality turns into equality).
\end{itemize}
